Framework for Unified Optimal Synthesis of Planar Mechanisms for Motion and Path Generation using Shape Optimization

### 2018-03-07 idetc2018.tex
Bug fixes

Original contribution of this paper are in 1) a novel objective function for defect-free motion generation problem, 2) discovering a representation of coupler motion and path which is invariant under similarity transformations (henceforth termed as motion signature and path signature respectively.), 3) novel algorithm for partial matching of motions , 3) optimal storage by means of auto-encoder neural network and efficient neighbor search in the clustered database.
The objective function that drives the synthesis process computes a distance measure of dissimilarity between the task motion and the coupler motion generated by current linkage parameters.
In contrast to precision point method where distance measure is in terms of interpolation error, the distance measure of dissimilarity is valid between two planar curves or motions.
Which inherently requires the continuity of output; ensuring the output mechanism defect free throughout the task.

@@

Similarly, we can formulate motion synthesis as,
\begin{equation}\label{objectiveFunMotion}
  \argminA_{\textbf{\emph{l}}, W_i} (E_{min}(p, W_i)
\end{equation}
Here, E is the Dissimilarity function from eq.~\req{mccEq} while p and ${\{W_i\}}_{i=0}^{s}$ are motion signatures instead of path signatures.

@@

Objective function evaluation step consists of calculation of coupler motion or path and finding its dissimilarity score.
It is important to note that representation obtained in Section~\ref{sec_sign} reduces size of the linkage parameters in optimization.
This optimization problem can be solved using search methods which do not require gradient computation.
We can employ global optimization methods such as differential evolution at the start and local optimization methods link Powell's method towards the end for faster convergence\cite{ullah1997}.
Section~\ref{examples} presents results for the optimization technique used.

@@

Once a network is trained, Output of the bottle-neck layer $(h_{ib})$ represents the compressed feature space ($Z$).
It can be seen that input information is compressed by a factor of 10, while achieving $95\%$ reconstruction accuracy.
Standard clustering algorithms are performed on this latent space for better clustering\cite{song2013}.
We use Agglomerative Clustering, a method of Hierarchical clustering, which is an approach to partitioning clustering for identifying groups in the dataset.
\emph{Ward}\cite{ward1963} Linkage criterion is used for clustering, which minimizes the variance of the clusters being merged.
The distance metric used is the euclidean distance in the latent space.
Although the more accurate distance metric is distance function discussed in sec.~\ref{sec_distanceMetric}, it is very expensive to calculate it for entire database.
Signatures with ${O}(m)$ points, take ${O}(m\log{}m)$ time for each comparisons and there are ${O}(N^2)$ number of comparisons to be made for database of $N$ points.
When user raises one such query, we first find k nearest neighbors among $1500$ cluster centers, then descend into their clusters if needed.
Motion with highest similarity score is returned along with its corresponding linkage parameters which if required, are further fine-tuned to match the query using local optimization.

@@

\section{Examples}\label{sec_example}
This sections presents a case study presenting the effectiveness of our approach.
The task is to find a pool of linkage systems that can perform snow-shoveling with a motion shown in Fig.~\ref{motionQuery}.
The motion data is tabulated in Table ~\ref{poseData} which we fit into a B-spline with arc-length parameterization.
The task can be treated as a finite position motion generation and solved for valid solutions.
We try with our real time computational methods of algebraic fitting\cite{generalfitting-JCISE},\cite{deshpande2017} but the solutions obtained suffer from circuit defect.
Now we employ the approach presented in this paper.
First step is to calculate motion signature of the task motion.
For that we follow the steps given in section~\ref{sec_sign} to obtain the motion signature depicted in Fig.~\ref{queryResult}.
Next we raise the signature query for nearest signatures among the cluster centers of the database.
Fig.\ref{queryResult} shows nine nearest neighbor signatures along with task signature.
Table ~\ref{knnLinkageData} presents the linkage parameters corresponding to the nearest neighbors along with their distance score from the task.
Coupler motions of these linkages have a part which matches with the shape of input motion query.
Actual scaling and orientation of the linkage can be found out easily by comparing analogous points which are given by the offset index $j$ that corresponds to minimum distance$(E_min)$ in eq.~\req{mccEq}.
Figures~\ref{knnSol1} to \ref{knnSol7} depict the solutions obtained after scaling and orienting the linkage to match required motion.
Although all of these linkages satisfactorily perform the input task with any defect, linkages in Fig.~\ref{knnsol1}, \ref{knnsol2}, \ref{knnsol3}, \ref{knnsol7} are suitable for the task considering the pivot locations.
Nevertheless this approach produces a large variety of solutions which otherwise would have been very hard to found using precision point approach.

@@

\begin{figure}
\centering
\includegraphics[width=240pt]{figure/sol7.eps}
  \caption{Eighth Linkage in the table~\ref{knnLinkageData} and its resultant motion.}
\label{knnSol8}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=240pt]{figure/sol7.eps}
  \caption{Eighth Linkage in the table~\ref{knnLinkageData} and its resultant motion.}
\label{knnSol9}
\end{figure}

>>>>

Original contribution of this paper are in 1) a novel objective function for defect-free motion generation problem, 2) discovering a representation of coupler motion and path which is invariant under similarity transformations (henceforth termed as motion signature and path signature respectively.), 3) novel algorithm for partial matching of motions , 4) optimal storage by means of auto-encoder neural network and efficient neighbor search in the clustered database.
The objective function that drives the synthesis process computes a distance measure of dissimilarity between the task motion and the coupler motion generated by current linkage parameters.
In contrast to precision point method where distance measure is in terms of interpolation error, the distance measure of dissimilarity is valid between two planar curves or motions.
Which inherently requires the continuity of output; ensuring the output mechanism defect free throughout the task.

@@

Similarly, we can formulate motion synthesis as,
\begin{equation}\label{objectiveFunMotion}
  \argminA_{\textbf{\emph{l}}, W_i} (E_{min}(p, W_i))
\end{equation}
Here, E is the Dissimilarity function from eq.~\req{mccEq} while p and ${\{W_i\}}_{i=0}^{s}$ are motion signatures instead of path signatures.

@@

Objective function evaluation step consists of calculation of coupler motion or path and finding its dissimilarity score.
It is important to note that representation obtained in Section~\ref{sec_sign} reduces size of the linkage parameters in optimization.
This optimization problem can be solved using search methods which do not require gradient computation.
We can employ global optimization methods such as differential evolution at the start and local optimization methods link Powell's method towards the end for faster convergence\cite{ullah1997}.
%Section~\ref{examples} presents results for the optimization technique used.

@@

Once a network is trained, Output of the bottle-neck layer $(h_{ib})$ represents the compressed feature space ($Z$).
As the bottleneck layer has 10 neurons and input is 100 dimensional vector, it is evident that information is compressed by a factor of 10, while achieving $95\%$ reconstruction accuracy.
Standard clustering algorithms are performed on this latent\footnote{compressed output of bottleneck layer.} space for better clustering\cite{song2013}.
We use Agglomerative Clustering, a method of Hierarchical clustering, which is an approach to partitioning clustering for identifying groups in the dataset.
\emph{Ward}\cite{ward1963} Linkage criterion is used for clustering, which minimizes the variance of the clusters being merged.
The distance metric used is the euclidean distance in the latent space.
Although the more accurate distance metric is distance function discussed in sec.~\ref{sec_distanceMetric}, it is very expensive to calculate it for entire database.
Signatures with ${O}(m)$ points, take ${O}(m\log{}m)$ time for each comparisons and there are ${O}(N^2)$ number of comparisons to be made for database of $N$ points.
When user raises one such query, we first find k nearest neighbors among $1500$ cluster centers, then descend into their clusters if needed.
Motion with highest similarity score is returned along with its corresponding linkage parameters which if required, are further fine-tuned to match the query using local optimization.

@@

\section{Examples}\label{sec_example}
This sections presents a case study presenting the effectiveness of our approach.
The task is to find a pool of linkage systems that can perform snow-shoveling with a motion shown in Fig.~\ref{motionQuery}.
The motion data is tabulated in Table ~\ref{poseData} which we fit into a B-spline with arc-length parameterization.
The task can be treated as a finite position motion generation and solved for valid solutions.
We try with our real time computational methods of algebraic fitting\cite{generalfitting-JCISE},\cite{deshpande2017} but the solutions obtained suffer from circuit defect.
Now we employ the approach presented in this paper.
First step is to calculate motion signature of the task motion.
For that we follow the steps given in section~\ref{sec_sign} to obtain the motion signature depicted in Fig.~\ref{queryResult}.
Next we raise the signature query for nearest signatures among the cluster centers of the database.
Fig.\ref{queryResult} shows nine nearest neighbor signatures along with task signature.
Table ~\ref{knnLinkageData} presents the linkage parameters corresponding to the nearest neighbors along with their distance score from the task.
Coupler motions of these linkages have a part which matches with the shape of input motion query.
Actual scaling and orientation of the linkage can be found out easily by comparing analogous points which are given by the offset index $j$ that corresponds to minimum distance$(E_min)$ in eq.~\req{mccEq}.
Figures~\ref{knnSol1} to \ref{knnSol7} depict the solutions obtained after scaling and orienting the linkage to match required motion.
Although all of these linkages satisfactorily perform the input task with any defect, linkages except Fig.~\ref{knnSol4}, \ref{knnSol5}, \ref{knnSol6} are suitable for the task considering the pivot locations.
Nevertheless this approach produces a large variety of solutions which otherwise would have been very hard to found using precision point approach.

@@

\begin{figure}
\centering
\includegraphics[width=240pt]{figure/sol8.eps}
  \caption{Eighth Linkage in the table~\ref{knnLinkageData} and its resultant motion.}
\label{knnSol8}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=240pt]{figure/sol9.eps}
  \caption{Ninth Linkage in the table~\ref{knnLinkageData} and its resultant motion.}
\label{knnSol9}
\end{figure}
